Tree size, exposure, and hydraulic traits interactively shape drought response in a temperate broadleaf forest

### 2019-06-07 manuscript/03-methods.Rmd
Added more files to make book for article

Research was conducted at the Smithsonian Conservation Biology Institute (SCBI) in Virginia, USA, with cores taken from trees on the 25.6 ha ForestGEO (Global Earth Observatory) study plot (Anderson-Teixeira 2015). SCBI (38°53'36.6"N, 78° 08'43.4"W) (Gonzalez-Akre et al 2016) is located in the central Appalachian Mountains at the northern edge of Shenandoah National Park. Primary forest composition in the plot is oak-hickory, while elevations range from 273-338m above sea level (Gonzalez-Akre 2016) with a topographic relief of 65m (Bourg et al 2013).

## Data Collection
Cores were collected in 2010-2011 or 2016-2017 from a breast height of 1.3m using a 5mm increment borer. Live trees were selected at random from each species in 2010-2011, with at least 30 of those trees having a diameter at breast height (DBH) of at least 10cm (Bourg et al 2013). In 2016-2017, cores were collected from all dead trees found in the annual mortality census (Gonzalez-Akre et al 2016). They were sanded, measured, and standardized in the same process as seen in Helcoski et al 2019.

@@

- sapwood ratio

>>>>

Research was conducted at the Smithsonian Conservation Biology Institute (SCBI) in Virginia, USA, with cores taken from trees on the 25.6 ha ForestGEO (Global Earth Observatory) study plot [@andersonteixeira_ctfs-forestgeo:_2015]. SCBI (38°53'36.6"N, 78° 08'43.4"W) [@gonzalezakre_patterns_2016] is located in the central Appalachian Mountains at the northern edge of Shenandoah National Park. Primary forest composition in the plot is oak-hickory, while elevations range from 273-338m above sea level [@gonzalezakre_patterns_2016] with a topographic relief of 65m (Bourg et al 2013).

## Data Collection
Cores were collected in 2010-2011 or 2016-2017 from a breast height of 1.3m using a 5mm increment borer. Live trees were selected at random from each species in 2010-2011, with at least 30 of those trees having a diameter at breast height (DBH) of at least 10cm (Bourg et al 2013). In 2016-2017, cores were collected from all dead trees found in the annual mortality census [@gonzalezakre_patterns_2016]. They were sanded, measured, and standardized in the same process as seen in Helcoski et al 2019.

@@

Height sources include [@stovall_assessing_2018], [@stovall_terrestrial_2018], [@andersonteixeira_ctfs-forestgeo:_2015],
